**Density Dependence**

### 2023-03-04 Rmd/mseMac.Rmd
removed saves

```{r}
save(om,eqM,rfpts,params,file="~/Desktop/tmp/t.RData")
```

```{r, projections-1}
load("~/Desktop/tmp/t.RData")
source("/home/laurie/Desktop/projects/ddmse/R/dd.R")

@@

```{r}
save(prjs,file="~/Desktop/tmp/t.RData")

load("~/Desktop/tmp/t.RData")

smry=mdply(names(prjs), function(x) mdply(names(prjs[[x]]),
            function(y) cbind(A=x,B=y,model.frame(FLQuants(prjs[[x]][[y]][,"2040"], F=fbar,SSB=ssb,Catch=catch),drop=T))))
cast(ddply(smry,.(A,B), with, data.frame(F=median(F),SSB=median(SSB),Catch=median(Catch),F=median(F))),A~B,value="F")
cast(ddply(smry,.(A,B), with, data.frame(F=median(F),SSB=median(SSB),Catch=median(Catch),F=median(F))),A~B,value="Catch")
```

>>>>

```{r, projections-1}
source("/home/laurie/Desktop/projects/ddmse/R/dd.R")

@@

```{r}
smry=mdply(names(prjs), function(x) mdply(names(prjs[[x]]),
            function(y) cbind(A=x,B=y,model.frame(FLQuants(prjs[[x]][[y]][,"2040"], F=fbar,SSB=ssb,Catch=catch),drop=T))))
cast(ddply(smry,.(A,B), with, data.frame(F=median(F),SSB=median(SSB),Catch=median(Catch),F=median(F))),A~B,value="F")
cast(ddply(smry,.(A,B), with, data.frame(F=median(F),SSB=median(SSB),Catch=median(Catch),F=median(F))),A~B,value="Catch")
```
